---
title: "Memory Cue Duration and Directed Forgetting"
author: "Kyle Kurkela and Nancy Dennis"
date: '`r Sys.Date()`'
output: html_notebook
params:
  datapath: ./data/
---

# Load Libraries

```{r libraries, message=FALSE, warning=FALSE}

library('tidyverse')
library('knitr')
library('tables')

```

# Load Data

```{r load_data}

# Initalize variables
datapath           <- params$datapath
ya_raw_data_file   <- paste0(datapath, "ya_raw_data.csv")
oa_raw_data_file   <- paste0(datapath, "oa_raw_data.csv")
demo_raw_data_file <- paste0(datapath, "demographics.csv")

# Load data into dataframes
df.young        <- read.csv(ya_raw_data_file, quote = "\'")
df.old          <- read.csv(oa_raw_data_file, quote = "\'")
df.demographics <- read.csv(demo_raw_data_file, quote = "\'")

```

# Data Cleaning

## Demographics

1. Drop Empty Variables  
2. Create EDUCATION_yrs variable, which calculates the EDUCATION variable in terms of years of schooling  
3. Compute a composite Cognitive Assessment variable by calculating the mean (rounded to 2 decimal points) of the each subject's Symbol Search, Digit-Symbol, Arithmetic, Letter-Number Sequencing, and Vocabulary scores 

```{r clean_demographics_data}

# dropping blank variables; creating EDUCTION_yrs
df.demographics %>%
  select(-X, -X.1) %>%
  mutate(EDUCATION_yrs = ifelse(EDUCATION == '8th grade', 8,
                                ifelse(EDUCATION == '9th grade', 9, 
                                       ifelse(EDUCATION == '10th grade', 10,
                                              ifelse(EDUCATION == '11th grade', 11,
                                                     ifelse(EDUCATION == '12th grade', 12,
                                                            ifelse(EDUCATION == '1 yr college' | EDUCATION == '1 Year college' | EDUCATION == '1 year college', 13,
                                                                   ifelse(EDUCATION == '2 yrs college' | EDUCATION == '2 Years college' | EDUCATION == '2 years college', 14,
                                                                          ifelse(EDUCATION == '3 yrs college' | EDUCATION == '3 Years college' | EDUCATION == '3 years college', 15,
                                                                                 ifelse(EDUCATION == '4 yrs college' | EDUCATION == '4 Years college' | EDUCATION == '4 years college', 16,
                                                                                        ifelse(EDUCATION == 'Post-grad work', 17,
                                                                                               ifelse(EDUCATION == 'Masters', 18,
                                                                                                      ifelse(EDUCATION == 'Doctoral', 20, NA)))))))))))),
         Sex = ifelse(Sex == 'F', 'Female', 
                      ifelse(Sex == 'M', 'Male', NA))) -> df.demographics 

# Force Age and Sex variables into the all capitalization variable name convention
colnames(df.demographics)[10:11] <- c("AGE", "SEX")

# Calculating Cognitive Assessment Composite Score
df.demographics %>%
  rowwise() %>%
  mutate(COG_ASSESS = mean(c(SYMBOLSEARCH, DIGITSYMBOL, DIGITSPAN, ARITHMETIC, LNSEQUENCING, VOCAB), na.rm = TRUE),
         COG_ASSESS = round(COG_ASSESS, digits = 2)) -> df.demographics

```

## Raw Experimental Data

1. Concatenate the young and old data, creating a new factor AgeGroup  
2. Drop the extra jitter varaiable  
3. Make the numeric coding schemes factors with informative levels  

```{r concatenate_and_clean, warning=FALSE}

# concatenate
df.all <- bind_rows(list(df.young, df.old), .id = "AgeGroup")

# cleans
df.all %>%
  select(-jit.1) %>%
  mutate(
    enctype  = ifelse(enctype == 1, '1 Second',
                    ifelse(enctype == 2, '3 Seconds', 
                           ifelse(enctype == 3, '5 Seconds', 'Lure'))),
    enctype  = factor(enctype),
    score    = ifelse(score == 1, 'Remember',
                     ifelse(score == 2, 'Know',
                            ifelse(score == 3, 'New', 'No Response'))),
    score    = factor(score),
    Response = ifelse(Response == 2, 'B Key',
                      ifelse(Response == 22, 'V Key',
                             ifelse(Response == 14, 'N Key', 'No Response'))),
    Response = factor(Response),
    type     = ifelse(type == 0, 'To Be Forgotten', 
                      ifelse(type == 1, 'To Be Remembered', 'Lure')),
    type     = factor(type),
    AgeGroup = ifelse(AgeGroup == 1, 'Young', 
                      ifelse(AgeGroup == 2, 'Old', NA)),
    AgeGroup = factor(AgeGroup)
  ) -> df.all

```

# Combine Demographics and Experimental Data

```{r add_demographics, warning=FALSE}

(df.CDur <- left_join(df.all, df.demographics, by = c("subject" = "SUBJECT")))

```

# Figure 1: Demographics Summary Table

```{r demographics_summary}

df.CDur %>%
  group_by(AgeGroup) %>%
  summarise_at(vars(AGE, MMSE, SYMBOLSEARCH, DIGITSYMBOL, DIGITSPAN, ARITHMETIC, LNSEQUENCING, VOCAB, COG_ASSESS), funs(mean), na.rm = TRUE) %>%
  mutate_at(vars(-AgeGroup), round, digits = 2) %>%
  gather(key = Measure, value = Mean, AGE:COG_ASSESS, factor_key = TRUE) -> table1

# filter(table1, AgeGroup == "Young") %>%
#   select(Measure, Mean) -> Young
# filter(table1, AgeGroup == "Old") %>%
#   select(Measure, Mean) -> Old
# 
# table1 <- inner_join(Young, Old, by = c('Measure'), suffix = c('_Young', '_Old'))

# ftable(table1, col.vars = c(1), row.var =  )

```

```{r}


```


