---
title: "Memory Cue Duration and Directed Forgetting"
author: "Kyle Kurkela and Nancy Dennis"
date: '`r Sys.Date()`'
output: 
  html_notebook:
    code_folding: hide  
    toc: true
    toc_float: true
    number_sections: true
params:
  datapath: ~/Documents/MATLAB/githubrepos/personal-repos/CDur/data/
---

# Loading Libraries

For the purposes of this notebook, I will be using the `tidyverse` and `knitr` packages.

```{r libraries, message=FALSE, warning=FALSE}
library('tidyverse')
library('knitr')
library('emmeans')
library('kableExtra')
```

# Load Data

Load the raw data into R from the datapath directory input at the top of the notebook.

```{r load}
# Initalize variables
datapath           <- params$datapath
ya_raw_data_file   <- paste0(datapath, "ya_raw_data.csv")
oa_raw_data_file   <- paste0(datapath, "oa_raw_data.csv")
demo_raw_data_file <- paste0(datapath, "demographics.csv")

# Load data into dataframes
df.young        <- read.csv(ya_raw_data_file, quote = "\'")
df.old          <- read.csv(oa_raw_data_file, quote = "\'")
df.demographics <- read.csv(demo_raw_data_file, quote = "\'")

# Remove problem subjects o322, o122, and o307
df.old          <- filter(df.old, subject != 'o322')
df.old          <- filter(df.old, subject != 'o122')
df.old          <- filter(df.old, subject != 'o307')

df.demographics <- filter(df.demographics, SUBJECT != 'o322')
df.demographics <- filter(df.demographics, SUBJECT != 'o122')
df.demographics <- filter(df.demographics, SUBJECT != 'o307')
```

# Data Cleaning

## Demographics

In this section of the notebook, we will be cleaning up the demographics data by:  

1. Droping empty variables.  
2. Creating the `EDUCATION_yrs` variable, which calculates the `EDUCATION` variable in terms of years of schooling.  
3. Forcing the `AGE` and `SEX` variables to follow the all capitialization variable naming convention of this notebook.  
4. Compute the composite `BASELINE_COGITIVE_ABILITY` variable by calculating the mean (rounded to 2 decimal points) of the each subject's Symbol Search, Digit-Symbol, Arithmetic, Letter-Number Sequencing, and Vocabulary scores. 

```{r clean_demographics_data}
# dropping blank variables; creating EDUCTION_yrs
df.demographics %>%
  select(-X, -X.1) %>%
  mutate(EDUCATION_yrs = ifelse(EDUCATION == '8th grade', 8,
                         ifelse(EDUCATION == '9th grade', 9, 
                         ifelse(EDUCATION == '10th grade', 10,
                         ifelse(EDUCATION == '11th grade', 11,
                         ifelse(EDUCATION == '12th grade', 12,
                         ifelse(EDUCATION == '1 yr college' | 
                                EDUCATION == '1 Year college' | 
                                EDUCATION == '1 year college', 13,
                         ifelse(EDUCATION == '2 yrs college' | 
                                EDUCATION == '2 Years college' | 
                                EDUCATION == '2 years college', 14,
                         ifelse(EDUCATION == '3 yrs college' | 
                                EDUCATION == '3 Years college' | 
                                EDUCATION == '3 years college', 15,
                         ifelse(EDUCATION == '4 yrs college' | 
                                EDUCATION == '4 Years college' | 
                                EDUCATION == '4 years college', 16,
                         ifelse(EDUCATION == 'Post-grad work', 17,
                         ifelse(EDUCATION == 'Masters', 18,
                         ifelse(EDUCATION == 'Doctoral', 20, NA)))))))))))),
         Sex = ifelse(Sex == 'F', 'Female', 
               ifelse(Sex == 'M', 'Male', NA))) -> df.demographics 

# Force Age and Sex variables into the all capitalization variable name convention
colnames(df.demographics)[10:11] <- c("AGE", "SEX")

# Calculating Cognitive Assessment Composite Score
df.demographics %>%
  rowwise() %>%
  mutate(BASELINE_COGITIVE_ABILITY = mean(c(SYMBOLSEARCH, 
                                            DIGITSYMBOL, 
                                            DIGITSPAN, 
                                            ARITHMETIC, 
                                            LNSEQUENCING, 
                                            VOCAB), na.rm = TRUE),
         BASELINE_COGITIVE_ABILITY = round(BASELINE_COGITIVE_ABILITY, digits = 2)) %>%
  ungroup() -> df.demographics

# Calculate the Composite Z score
CompositeVars <- c('SYMBOLSEARCH', 'DIGITSYMBOL', 'DIGITSPAN', 'ARITHMETIC', 'LNSEQUENCING', 'VOCAB')

df.demographics %>%
  mutate(AgeGroup = str_extract(string = SUBJECT, pattern = '^[yo]'),
         AgeGroup = factor(AgeGroup, levels = c('y', 'o'), labels = c('Young Adults', 'Old Adults'))) %>%
  group_by(AgeGroup) %>%
  mutate_at(CompositeVars, scale) %>%
  ungroup() %>%
  mutate(COMPOSITEZSCORE = pmap_dbl(select(., one_of(CompositeVars)), lift_vd(mean))) -> df.demographics.z
```

## Raw Experimental Data

In this section of the notebook we will be cleaning the raw experimental data by:  

1. Concatenating the young and old data and creating a new variable `AgeGroup`.    
2. Dropping the extra jitter varaiable.  
3. Making the numeric coding of variables `enctype`, `score`, `Response`, `type`, and `AgeGroup` into factors with informative level names.  

```{r concatenate_and_clean, warning=FALSE}
# concatenate
df.all <- bind_rows(list(df.young, df.old), .id = "AgeGroup")

# clean
df.all %>%
  select(-jit.1) %>% # dropping extra jitter
  mutate(
    enctype  = ifelse(enctype == 1, '1 Second',
               ifelse(enctype == 3, '3 Seconds', 
               ifelse(enctype == 5, '5 Seconds', 'Lure'))),
    enctype  = factor(enctype),
    score    = ifelse(score == 1, 'Remember',
               ifelse(score == 2, 'Know',
               ifelse(score == 3, 'New', 'No Response'))),
    score    = factor(score),
    Response = ifelse(Response == 2, 'B Key',
               ifelse(Response == 22, 'V Key',
               ifelse(Response == 14, 'N Key', 'No Response'))),
    Response = factor(Response),
    type     = ifelse(type == 0, 'To Be Forgotten', 
               ifelse(type == 1, 'To Be Remembered', 'Lure')),
    type     = factor(type),
    AgeGroup = ifelse(AgeGroup == 1, 'Young', 
               ifelse(AgeGroup == 2, 'Old', NA)),
    AgeGroup = factor(AgeGroup)
  ) -> df.all
```

# Demographics Summary

Next, lets re-create the Demographics Summary Table: 

```{r demographics_summary, warning=FALSE}

# take the demographics data frame and..
df.demographics %>%
  mutate(AgeGroup = str_extract(SUBJECT, '^[oy]'),
         AgeGroup = factor(AgeGroup, levels = c('y', 'o'), labels = c('Younger Adults', 'Old Adults'))) %>%
  select(-SUBJECT) %>% # drop the SUBJECT variable
  group_by(AgeGroup) %>% # group by AgeGroup
  summarize_if(is.numeric, mean, na.rm = TRUE) %>% # Calculate a mean of every numeric variables
  mutate_if(is.numeric, round, digits = 2) %>% # round all of the numeric variables to 2 decimal places
  gather(key=Measure, value=Mean, -AgeGroup) ->  temp

# Break this newly cleaned demographic dataframe into OAs and YAs
temp %>%
 filter(AgeGroup == "Old Adults") -> OAs
temp %>%
  filter(AgeGroup == "Younger Adults") -> YAs

# Join the OAs and YAs dataframes into a single table
table1.demographics  <- left_join(select(OAs, -AgeGroup), select(YAs, -AgeGroup), 
                                  by = c("Measure"), 
                                  suffix = c("_OA", "_YA"), "-AgeGroup")

# Rename the Top of the Table
names(table1.demographics) <- c("Measure", "Older Adults", "Younger Adults")

# Rename the 9th and 10th variables EDUCATION and COMPOSTIE
table1.demographics[9,1]  <- "EDUCATION"
table1.demographics[10,1] <- "COMPOSITE"

# Display the Table
table1.demographics

```

Kyle's Notes:  

- All of the above summary statistics are the mean of each measure for each age group  
- The Younger Adults did NOT complete the MMSE, so their score appears here as `NaN`  

# DF-Effect

The first question we want to answer statistically: Do we see the `Directed-Forgetting Effect` in ANY of our experimental conditions?

First, lets calculate the `Directed-Forgetting Effect`:  

```{r DF_calculations}
# Calculate the miss rates
df.all %>%
  filter(enctype != "Lure") %>%
  mutate(enctype = factor(enctype)) %>%
  group_by(AgeGroup, enctype, type, subject) %>%
  summarize(MissRate = mean(score == "New")) %>% ungroup() -> df.missrates

# Break the dataframe into TBF and TBR
df.missrates %>% filter(type == "To Be Forgotten") %>% select(-type) -> TBF.Forgotten
df.missrates %>% filter(type == "To Be Remembered") %>% select(-type) -> TBR.Forgotten

# Merge join the TBF and TBR data frames together, making a "wide" dataframe
df.DFeffects <- left_join(TBF.Forgotten, TBR.Forgotten, 
                          by = c('AgeGroup','enctype', 'subject'), 
                          suffix = c("TBF", "TBR"))

# Calculate the DF-Effect
df.DFeffects %>%
  transmute(
    AgeGroup = AgeGroup,
    enctype = enctype,
    subject = subject,
    DF.effect = MissRateTBF - MissRateTBR) -> df.DFeffects
```

Now, to answer the question above we want to perform a series of Bonferroni corrected, one-sided, one-sample t-tests comparing the means of each cell of our experimental design to see if they are signifcantly greater than 0.  

## By Condition By Age Group

```{r}
# A Visual
df.DFeffects %>%
  group_by(enctype, AgeGroup) %>%
  summarize(meanDF.effect = mean(DF.effect), semDF.effect = sd(DF.effect)/sqrt(n())) %>%
  ggplot(aes(x = AgeGroup, y = meanDF.effect, group = enctype, fill = enctype)) + 
  geom_bar(stat="identity", position = position_dodge(width = .95)) + 
  geom_errorbar(aes(ymin = meanDF.effect - semDF.effect, ymax = meanDF.effect + semDF.effect), 
                width = 0.2, 
                position = position_dodge(width = .95)) + 
  scale_fill_brewer(palette = "Set2") + 
  scale_y_continuous(limits = c(0, NA), expand = c(0, 0, .05, 0)) + 
  ggtitle("Directed Forgetting Effect Across Experiment") + 
  ylab("Effect Size") + xlab("Age Group") + 
  labs(fill = 'Cue Duration') +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.ticks.x = element_blank(), 
        axis.text.x = element_text(size = 12))
```

The results of the **Age Group x Cue Duration ANOVA** breakdown as follows:  

```{r ANOVA}
# ANOVA
m <- aov(DF.effect ~ AgeGroup*enctype + Error(subject/enctype), data = df.DFeffects)

# Summarize, break into between and repeated factors
object   <- summary(m)
DF.between  <- object$`Error: subject`[[1]]
DF.repeated <- object$`Error: subject:enctype`[[1]]
object
```

1.) The main effect of `AgeGroup` is **NOT** signifcant (F(`r DF.between$Df[[1]]`) = `r round(DF.between$'F value'[[1]], digits = 2)`, p = `r round(DF.between$'Pr(>F)'[[1]], digits = 2)`).  
2.) The main effect of `CueDuration` **IS** significant (F(`r DF.repeated$Df[[1]]`) = `r round(DF.repeated$'F value'[[1]], digits = 2)`, p < `r if(DF.repeated$'Pr(>F)'[[1]] < .001) (.001)`).  
3.) The interaction between `AgeGroup` and `CueDuration` was **NOT** signifcant (F(`r DF.repeated$Df[[2]]`) = `r round(DF.repeated$'F value'[[2]], digits = 2)`, p = `r round(DF.repeated$'Pr(>F)'[[2]], digits = 2)`).  

```{r}
# A prori tests using EMMEANS

# Question: is there a Directed Forgetting Effect > 0 for each AgeGroup / Cue Duration?

require(emmeans)
emmeans(m, ~ AgeGroup + enctype) -> EMMEANS.DF

summary(EMMEANS.DF, digits = 2, infer = T, adjust = 'bonferroni', side = '>')
```

Observing the table above, it appears that there is a statistically significant DF effect for both AgeGroups in the 3 and 5 second conditions. There is NOT, however, a statistically significant effect for either AgeGroup in the 1 Second Cue duration group.  

```{r}
# a posterior contrasts using EMMEANS

# Is there a linear effect in OAs? A Quadratic effect in YAs?

require(emmeans)
emmeans(m, ~ AgeGroup + enctype) -> EMMEANS.DF

contrast(EMMEANS.DF, method = 'poly', by = 'AgeGroup')
```

There is a significant linear trend for YAs and OAs and a significant quadratic trend for YAs.

## With Cog Assess Score

What do our results look like when we consider baseline cognitive assessment score?

```{r Visual, warning=FALSE}
cog.assess.composites <- select(df.demographics.z, SUBJECT, COMPOSITEZSCORE)
cog.assess.composites <- transmute(cog.assess.composites, subject = SUBJECT, 
                                   composite = COMPOSITEZSCORE)

df.DFeffects <- left_join(df.DFeffects, cog.assess.composites, by = "subject")

ggplot(df.DFeffects, aes(y = DF.effect, x = composite, colour = AgeGroup)) + 
  scale_colour_brewer(palette = "Set2") + 
  geom_point() + 
  facet_grid(AgeGroup ~ enctype) + 
  geom_smooth(method = "lm", formula = y ~ x, se = TRUE, colour = "navyblue", linetype = "longdash")
```

Run a linear regression model with all three predictors.  

```{r regression}
regression.model <- lm(DF.effect ~ AgeGroup*enctype*composite, data = df.DFeffects)

anova(regression.model)
```

```{r}
require(kableExtra)

df.DFeffects %>%
  group_by(AgeGroup, enctype) %>%
  nest_legacy() %>%
  mutate(regression = map(data, ~lm(DF.effect ~ composite, data = .x))) %>%
  mutate(regression.results = map(regression, broom::tidy)) %>%
  unnest_legacy(regression.results) %>%
  mutate_if(is.double, round, digits = 3) %>%
  kable(caption = 'DF Effect Linear Regressions within Groups') %>%
  kable_styling() %>%
  collapse_rows(columns = c(1,2), valign = 'top')
```


# Rec Effect

A second question we would like to answer is this: is there a signifcant `Recollection Effect`? The Recollection Effects operationalized as:  

`TBR-Rec - TBF-Rec`

This measure is similar too, but different than, the DF-Effect.

First, lets calculate the recollection effects:  

```{r rec-effect_calculations}
# calculate the Rec rates
df.all %>%
  filter(enctype != "Lure") %>%
  mutate(enctype = factor(enctype)) %>%
  group_by(AgeGroup, enctype, type, subject) %>%
  summarize(RecRate = mean(score == "Remember")) %>% ungroup() -> df.recrates

# Break the dataframe into TBF and TBR
df.recrates %>% filter(type == "To Be Forgotten") %>% select(-type)  -> TBF.Remembered
df.recrates %>% filter(type == "To Be Remembered") %>% select(-type) -> TBR.Remembered

# Merge join the TBF and TBR data frames together, making a "wide" dataframe
df.RecEffects <- left_join(TBF.Remembered, TBR.Remembered, 
                           by = c('AgeGroup','enctype', 'subject'), 
                           suffix = c("TBF", "TBR"))

# Calculate the Rec-Effect
df.RecEffects %>%
  transmute(
    AgeGroup = AgeGroup,
    enctype = enctype,
    subject = subject,
    Rec.effect = RecRateTBR - RecRateTBF) -> df.RecEffects
```

## By Condition By Age Group

```{r}
# A Visual
df.RecEffects %>%
  group_by(enctype, AgeGroup) %>%
  summarize(meanRec.effect = mean(Rec.effect), semRec.effect = sd(Rec.effect)/sqrt(n())) %>%
  ggplot(aes(x = AgeGroup, y = meanRec.effect, fill = enctype)) + 
  geom_bar(stat="identity", position = "dodge") + 
  geom_errorbar(aes(ymin = meanRec.effect - semRec.effect, ymax = meanRec.effect + semRec.effect), width = 0.2, position = position_dodge(.9)) + 
  scale_fill_brewer(palette = "Set2") + 
  scale_y_continuous(limits = c(0, .2)) + 
  ggtitle("Recollection Effect Across Experiment") + 
  ylab("Effect Size") + xlab("Cue Duration") + 
  theme(plot.title = element_text(hjust = 0.5))
```

The results of the **Age Group x Cue Duration ANOVA** breakdown as follows:

```{r}
# set sum to zero contrasts for Type III sums of squares calculation
contrasts(df.RecEffects$AgeGroup) <- contr.sum(nlevels(df.RecEffects$AgeGroup))
contrasts(df.RecEffects$enctype)  <- contr.sum(nlevels(df.RecEffects$enctype))

# ANOVA
m <- aov(Rec.effect ~ AgeGroup*enctype + Error(subject/enctype), data = df.RecEffects)

# Summarize, break into between and repeated factors
summary(m)
```

```{r}
# a prori tests against zero

require(emmeans)

emmeans(m, ~ AgeGroup + enctype) -> EMMEANS.RE

summary(EMMEANS.RE, infer = T, adjust = 'bonferroni', side = ">")
```

```{r}
# a posterior contrasts for linear and quadratic effects

require(emmeans)

emmeans(m, ~ AgeGroup + enctype) -> EMMEANS.RE

contrast(EMMEANS.RE, method = 'poly', by = 'AgeGroup')
```

## With Cog Asses Score

How do the results change when we add cognitive assessment score as a factor into our ANOVA?

```{r, warning=FALSE}
# A Visual
cog.assess.composites <- select(df.demographics.z, SUBJECT, COMPOSITEZSCORE)
cog.assess.composites <- transmute(cog.assess.composites, subject = SUBJECT, 
                                   composite = COMPOSITEZSCORE)

df.RecEffects <- left_join(df.RecEffects, cog.assess.composites, by = "subject")

ggplot(df.RecEffects, aes(y = Rec.effect, x = composite, colour = AgeGroup)) + 
  scale_colour_brewer(palette = "Set2") + 
  geom_point() + 
  facet_grid(AgeGroup ~ enctype) + 
  geom_smooth(method = "glm", se = TRUE, formula = y ~ x, colour = "navyblue", linetype = "longdash") +
  labs(title = "Recollection Effects", 
       subtitle = "As a function of Cue Duration, Age Group, and Cog Assess Score") + 
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
regression.model <- lm(Rec.effect ~ AgeGroup*enctype*composite, data = df.RecEffects)

anova(regression.model)
```


```{r rec.regression}
require(kableExtra)

df.RecEffects %>%
  group_by(AgeGroup, enctype) %>%
  nest_legacy() %>%
  mutate(regression = map(data, ~lm(Rec.effect ~ composite, data = .x))) %>%
  mutate(regression.results = map(regression, broom::tidy)) %>%
  unnest_legacy(regression.results) %>%
  mutate_if(is.double, round, digits = 3) %>%
  kable(caption = 'Rec Effect Linear Regressions within Groups') %>%
  kable_styling() %>%
  collapse_rows(columns = c(1,2), valign = 'top')
```